Spin canonical rings of log stacky curves

### 2016-01-08 curves-write-up/spin-cring.tex
curves: comment out a line causing error
curves: fix name of HJ

%\begin{figure}
%\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
%\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
\end{figure}
%\todo{Is this figure (figure 1)  still useful anywhere?}

@@

Literature on Cohn's geometric interpretation of hirzabruch jung fractions offers us an explicit formula for these primitives (Proposition 4.3 \todo{cite and add to bibtex}); one observes they all lie in degrees at most $\beta$ (since points in degree $\gamma=\beta+\omega$ can by written as a sum of points in degree $\beta$ with those in degree $\omega$).  Note that if two primitives had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$ and thus could not both be generators; thus all the $c_i$'s (their $y$ coordinates) are distinct, and we can thus order them with $c_i<c_{i+1}$ for all $i$.  Furthermore, note that in any degree $k$ greater than 1, there can be at most one new primitive, since we can construct points with $y$ coordinates between 0 and $\lfloor k\frac{\alpha}{\beta}\rfloor$ as a sum of elements in degree 1 and degree $k-1$, and these new primitives have pole order greater than all primitives of smaller $x$-coordinate.  Therefore, the ordering of primitives with $c_i<c_{i+1}$ for all $i$ also ensures that the $x$-values $k_i$'s are also in weakly increasing order.  Finally, let $y_1, \ldots, y_n$ be elements of $R_Lx$ with pole orders given by $c_1,\ldots, c_n$ and degrees given by the $x$ coordinates of the corresponding primitives.
%We will the use positive best lower approximations to
%construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
%
%Let 
%\[
%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
%	\beta}
%\]
%
%\noindent
%be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
%5Choose a positive best lower approximation $\frac{c_i}{k_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
%\[
%	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
%\]
%so the mediant inequality tells us
%\[
%	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
%\]
%Multiplying through by $k_i$ gives
%\[
%	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\%ord^{\halfcan'}_P(z_j) < c_i .
%\]

>>>>

%\begin{figure}
%\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
%\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
%\end{figure}
%\todo{Is this figure (figure 1)  still useful anywhere?}

@@

Literature on Cohn's geometric interpretation of Hirzebruch--Jung fractions offers us an explicit formula for these primitives (Proposition 4.3 \todo{cite and add to bibtex}); one observes they all lie in degrees at most $\beta$ (since points in degree $\gamma=\beta+\omega$ can by written as a sum of points in degree $\beta$ with those in degree $\omega$).  Note that if two primitives had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$ and thus could not both be generators; thus all the $c_i$'s (their $y$ coordinates) are distinct, and we can thus order them with $c_i<c_{i+1}$ for all $i$.  Furthermore, note that in any degree $k$ greater than 1, there can be at most one new primitive, since we can construct points with $y$ coordinates between 0 and $\lfloor k\frac{\alpha}{\beta}\rfloor$ as a sum of elements in degree 1 and degree $k-1$, and these new primitives have pole order greater than all primitives of smaller $x$-coordinate.  Therefore, the ordering of primitives with $c_i<c_{i+1}$ for all $i$ also ensures that the $x$-values $k_i$'s are also in weakly increasing order.  Finally, let $y_1, \ldots, y_n$ be elements of $R_Lx$ with pole orders given by $c_1,\ldots, c_n$ and degrees given by the $x$ coordinates of the corresponding primitives.
%We will the use positive best lower approximations to
%construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
%
%Let 
%\[
%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
%	\beta}
%\]
%
%\noindent
%be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
%5Choose a positive best lower approximation $\frac{c_i}{k_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
%\[
%	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
%\]
%so the mediant inequality tells us
%\[
%	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
%\]
%Multiplying through by $k_i$ gives
%\[
%	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\%ord^{\halfcan'}_P(z_j) < c_i .
%\]
